Wolbachia and Two Other Microbes Nobody Cares About That Changed The World Kinda

### 2015-12-16 paper.tex
cordy and its fuiting body

\usepackage{amstext}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
\usepackage{gensymb}
\usepackage{here}
\usepackage{caption}

@@

The story of how \textit{Ophiocordyceps} functions is a cycle, so you could start talking about it anywhere, but from an ant's perspective everything starts when it comes into contact with the spores of the fungus. The spores recognize they are on a host, and form a biological drill that utilizes enzymes and mechanical pressure to breach the ant's tough exoskeleton. Once inside, the fungus transforms into a yeast-like state, living in the hemocoel of the ant. [1] This is where the highly specialized adaptations of \textit{Ophiocordyceps} start to shine. There are many things that are unknown about how \textit{Ophiocordyceps} manipulates the mind of its host, but the outcome has been studied in depth. \textit{Ophiocordyceps} leads its host ant to the northern side of a sapling approximately 25 cm above the ground. There, the ant closes it mandibles on the bark of the sapling or the main vein on the bottom side of a leaf, never to open them again.

>>>>

\usepackage{amstext}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage[margin=1in, paperwidth=8.5in, paperheight=11in]{geometry}
%\usepackage{gensymb}
\usepackage{here}
\usepackage{caption}

@@

The story of how \textit{Ophiocordyceps} functions is a cycle, so you could start talking about it anywhere, but from an ant's perspective everything starts when it comes into contact with the spores of the fungus. The spores recognize they are on a host, and form a biological drill that utilizes enzymes and mechanical pressure to breach the ant's tough exoskeleton. Once inside, the fungus transforms into a yeast-like state, living in the hemocoel of the ant.\cite{cordy_infection} This is where the highly specialized adaptations of \textit{Ophiocordyceps} start to shine. There are many things that are unknown about how \textit{Ophiocordyceps} manipulates the mind of its host, but the outcome has been studied in depth. \textit{Ophiocordyceps} leads its host ant to the northern side of a sapling approximately 25 cm above the ground. There, the ant closes it mandibles on the bark of the sapling or the main vein on the bottom side of a leaf, never to open them again. It is there that the fungus rapidly colonizes the host, restructuring all nutrients available inside the host to produce a large fruiting body which grows out of the back of the ants head that will produce the spores to restart the cycle.\cite{life_of_dead_ant}
